---
title: "Example to gather the results from recon-all-clinical.sh outputs"
output: 
  html_notebook:
    toc: true
    toc_float: true
---

# libraries
```{r}
c('ggseg', 
  'tidyverse', 
  'furrr') |> 
  lapply(require, character.only = T)
```

# setting up multiple processors
```{r}
plan(multisession, workers = 4)
```

# gathering the following outputs
- aparc.stats (cortical measures in desikan killiany regions)
- aparc.a2009s.stats (cortical measures in destrieux regions)
- aparc.pial.stats (pial measures)
- aparc.DKTatlas.stats (cortical measures from regions of the desikan killiany tourville atlas)

Please change the paths to the appropriate input and output

- input /path/to/freesurfer_subjects_dir
- output /path/to/fs_measures_gathered.csv

```{r}
list(
  list("aparc.stats$",
       "aparc.a2009s.stats$",
       "aparc.pial.stats$",
       "aparc.DKTatlas.stats$"
  ),
  list("fs_cortical_measures_desikan_killay",
       "fs_cortical_measures_destrieux",
       "fs_cortical_pial_measures",
       "fs_dktatlas_measures"
  )
) |>
  future_pmap_dfr(~{
    read_atlas_files("/path/to/freesurfer_subjects_dir", ..1) |>
      pivot_longer(-c(subject, label), 
                   names_to = 'measure_name', 
                   values_to = 'measure_value') |> 
      mutate(measure_type = ..2)
  },
  .progress = T) |> 
  write.csv(paste0('/path/to/fs_measures_gathered.csv'),
            row.names = F,
            quote = F)
```
